---
title: "simpleRegress"
author: "Eden Williams"
date: "Summer 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## make a simple regression model

```{r}
bears <- read.csv(file="BEARS.csv",header = TRUE)
```

## Model LENGTH ~ NECK  this is an example  

```{r}
simp <- lm(LENGTH~NECK,data=bears)
plot(LENGTH~NECK,data=bears)
abline(simp)
summary.lm(simp)
```

## now predict the length of a bear who has a neck of 17, 22 and 26


```{r}
new <- data.frame(NECK=c(17,22,26))
predict(simp,new)
predict(simp,new,se.fit=TRUE)
```
## Surely there is another variable that can better predict LENGTH than NECK. Find one and compare its performance to that of neck by it value of Adjusted-Rsquared (bigger is better).

```{r}
chest <- lm(LENGTH~CHEST,data=bears)
plot(LENGTH~CHEST,data=bears)
abline(chest)
summary.lm(chest)
```
 The adjusted R-square for the CHEST model is 0.79. The model for the NECK model had an adjusted R-square of 0.75. The best model so far is the one based on CHEST

## Better Variables 

```{r}
age <- lm(LENGTH~AGE,data=bears)
plot(LENGTH~AGE,data=bears)
abline(age)
summary.lm(age)
```
Based upon adjusted R-squared value,which is 0.5073, AGE is not the best model.



```{r}
sex <- lm(LENGTH~SEX,data=bears)
plot(LENGTH~SEX,data=bears)
abline(sex)
summary.lm(sex)
```

Based upon adjusted R-squared value,which is -0.008373 , SEX is not the best model in predicting LENGTH.


```{r}
weight <- lm(LENGTH~WEIGHT,data=bears)
plot(LENGTH~WEIGHT,data=bears)
abline(weight)
summary.lm(weight)
```

Based upon the adjusted R-squared value,which is 0.7423, WEIGHT is a very similar model to NECK, which means it is not the best for predicting LENGTH. 

```{r}
head <- lm(LENGTH~HEADLEN,data=bears)
plot(LENGTH~HEADLEN,data=bears)
abline(head)
summary.lm(head)
```
Based upon the adjusted R-squared value,which is 0.8434, HEADLEN seems to be the best model for predicting LENGTH. 


```{r}
headw <- lm(LENGTH~HEADWTH,data=bears)
plot(LENGTH~HEADWTH,data=bears)
abline(headw)
summary.lm(headw)
```

Based upon the adjusted R squared value, which is 0.5321 , HEADWTH is not the best model for predicting LENGTH. 

## SUMMARY

Based upon the information presented above, the best model for predicting LENGTH, with an R squared value of 0.8434, is HEADLEN. 